\bf Hierarchical Network Structure Promotes Dynamical Robustness

### 2015-02-05 tex/overview.tex
add figure showing random Jacobians

We have derived an analytical expression for dynamical robustness, $R_{tot}$, of a network in terms of its interaction graph as a weighted average of the robustness of the SCCs, $R_i$, the corresponding number of links within each SCC, $d_i$, and the number of links between the SCCs, $l$ the entries of the Jacobian are sampled independently from a generic probability distribution. The expression in \ref{eq:sccrobustness} holds for the case of simultaneously perturbing any number of elements of the Jacobian, but can be schematized for the case of perturbing a single element as \ref{eq:robschematic} (see \reffigscc$\,$ for examples demonstrating this expression)
\begin{equation}\label{eq:robschematic}
R_{tot} = \frac{l+d_1 R_1 + d_2 R_2 + \cdots}{l+d_1 + d_2 + \cdots}.
\end{equation}
For instance, if our graph is the one in \reffigscc (middle panels), then we have two connected components, one with two nodes, and one with one node.  From \ref{tab:structstabmat}, we know that the graph with two nodes has probability $0.25$ of being stable and robustness $0.62$.  The graph with one node corresponds to a $1 \times 1$ matrix, so we have probability $0.5$ of stability and robustness $0.5$.  Thus, the probability of our 3-node graph being stable is $0.5 \times 0.25 = 0.125$ and its robustness is computed from \ref{eq:robschematic} in \reffigscc, which agrees with the value computed in \ref{tab:structstabmat} up to sampling error.

>>>>

We have derived an analytical expression for dynamical robustness, $R_{tot}$, of a network in terms of its interaction graph as a weighted average of the robustness of the SCCs, $R_i$, the corresponding number of links within each SCC, $d_i$, and the number of links between the SCCs, $l$. The entries of the Jacobian are sampled independently from a generic probability distribution. Examples of vector fields that may result from this sampling of Jacobian matrices are shown in \ref{fig:jacobianvectorfields}. The expression in \ref{eq:sccrobustness} holds for the case of simultaneously perturbing any number of elements of the Jacobian, but can be schematized for the case of perturbing a single element as \ref{eq:robschematic} (see \reffigscc$\,$ for examples demonstrating this expression)
\begin{equation}\label{eq:robschematic}
R_{tot} = \frac{l+d_1 R_1 + d_2 R_2 + \cdots}{l+d_1 + d_2 + \cdots}.
\end{equation}
For instance, if our graph is the one in \reffigscc (middle panels), then we have two connected components, one with two nodes, and one with one node.  From \ref{tab:structstabmat}, we know that the graph with two nodes has probability $0.25$ of being stable and robustness $0.62$.  The graph with one node corresponds to a $1 \times 1$ matrix, so we have probability $0.5$ of stability and robustness $0.5$.  Thus, the probability of our 3-node graph being stable is $0.5 \times 0.25 = 0.125$ and its robustness is computed from \ref{eq:robschematic} in \reffigscc, which agrees with the value computed in \ref{tab:structstabmat} up to sampling error.
